Continuous developmental change explains discontinuities in word learning

### 2020-03-20 journal/ms_blind.Rmd
revisions

header-includes:
   - \usepackage{tipa}
   - \usepackage[sortcites=false,sorting=none]{biblatex}

@@

figsintext        : no
figurelist        : yes
tablelist         : no
footnotelist      : no
lineno            : yes

@@

```{r load_packages, include = FALSE}
library(papaja)
library(png)
library(grid)
library(ggplot2)
library(ggthemes)
library(xtable)
options(xtable.comment = FALSE)
library(purrr)
library(readr)
library(ggplot2)
library(langcog)
library(boot)
#library(lazyeval)
library(dplyr)
library(tidyr)
library(wordbankr)
library(directlabels)
#library(scales)
library(stringr)
library(lmtest)
library(rwebppl)
library(jsonlite)
library(nlme)
library(feather)
library(broom)
library(HDInterval)
library(BBmisc)
library(stargazer)
library(lme4)
library(kableExtra)
```

#Introduction

@@

The probabilistic account has been put forward to explain patterns of learning and development at the qualitative level. However, it is crucial to have a precise computational instantiation of this account which would help us 1) test this theoretical hypothesis more directly and 2) identify the particular parameters that are the locus of developmental change.  One previous study attempted to provide such a computational instantiation [@hofer2017]. However, this previous work was designed with the goal of reproducing the results of a specific study [@pajak2016] which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.

@@

A similar probabilistic structure was used by @lewis2013 to model concept learning, and by @hofer2017 to model spoken word learning. However, the first study assumed that the sounds are heard unambiguously, and the second assumed the concepts are observed unambiguously. In our model, we assume that both labels and concepts are observed with a certain amount of perceptual noise, which we assume, for simplicity, is captured by a normal distribution:

@@

Finally, we assume there to be one-to-one mappings between concepts and labels and that observers have successfully learned these mappings during the exposure phase:
\begin{equation}
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{otherwise  }
\end{cases}
\end{equation}

@@

### Model 1
From the general expression \ref{eq:general}, we derive three exact analytical solutions instantiating different learning assumptions. Recall from expressions \ref{eq:object} and \ref{eq:sound} that $P(o|C)$ and $P(s|L)$ have parameters $\sigma_C$ and $\sigma_L$, respectively, that control perceptual uncertainty. The first solution is derived by assuming that the labels are recovered from sounds with a certain level of uncertainty $\sigma_L > 0$, but that concepts are unambiguously recovered from the observed objects, i.e., $\sigma_C \rightarrow 0$. This assumption has been made --- whether implicitly or explicitly --- by most previous work in this line of research. For example, in @stager1997, the objects were quite dissimilar. Thus, the assumption that they were easily discriminated by infants seems relatively well justified. One important implication of this assumption is that only the similarity of word sounds modulates success in word learning, not the similarity of the referents (as long as these referents are differentiated perceptually). This assumption yields the following probability function:

\begin{equation} \label{eq:model1}
P(o_T|s)= \frac{1}{1 + e^{-\frac{\Delta s^2}{2\sigma_L^2}}}
\end{equation}

where $\Delta s = s_2-s_1$.

### Model 2
The second solution is derived by making the more general assumption that both the labels and the concepts are recovered with noise from the sounds and objects. We first introduce the simplifying assumption that the label-related uncertainty $\sigma_L$ and the concept-related uncertainty $\sigma_C$ are of a similar magnitude, i.e., $\sigma_C \approx \sigma_L = \sigma$. This assumption makes the prediction that the sound similarity and the object similarity impact word learning accuracy in exactly the same way. Furthermore, it allows us to study the behavior of the model with only one free parameter, an important consideration given the small number of datapoints available from any given infant experiment.

\begin{equation} \label{eq:model2}
P(o_T|s)= \frac{1 + e^{- \frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}}{1 + e^{-\frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}+ e^{-\frac{\Delta s^2}{2\sigma^2}} + e^{-\frac{\Delta o^2}{2\sigma^2}}}
\end{equation}

@@

\begin{equation} \label{eq:model3}
P(o_T|s)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}
\end{equation}

In order to understand the predictions of the models (especially the more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation} show simulations of the accuracy $P(o_T|s)$ as a function of the distinctiveness parameters ($\Delta s$ and $\Delta o$) and the uncertainty parameters $\sigma_L$ and $\sigma_C$.

@@

plot_simulation <- ggplot(simulations, aes(x=x, y=y, col=sigma)) + 
  geom_line() + 
  theme_few()+
  theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 8),
      aspect.ratio = 0.7
      )+
  #plot.margin=grid::unit(c(0,0,0,0), "mm")
  ylim(c(0.4,1))+
  geom_hline(yintercept = 0.50, linetype="dashed") +
  xlab(expression(Delta*"s")) + ylab(expression("P("*o['T']*"| s)")) +
  facet_grid(.~obj) +
  #facet_grid(.~object_distance) +
  scale_color_discrete(name = expression(sigma))

@@

### Stimuli and similarity rating
The sound stimuli were generated using the MBROLA Speech Synthesizer [@dutoit1996]. We generated three kinds of nonsense word pairs which varied in their degree of perceptual similarity to English speakers: 1) *different* pairs: "lif"/"neem" and "zem"/"doof", 2) *intermediate* pairs: "aka"/"ama" and "ada"/"aba", and 3) *similar* non-English pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).

@@

###Design

@@

```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=4, fig.height=3, fig.cap = "Distances for both sound and object pairs from an adult norming study. Data represent Likert values normalized to [0,1] interval. Error bars represent 95\\% confidence intervals."}

@@

In the exposure trials, participants saw two objects associated with their corresponding sounds. We presented the first object on the left side of the tablet's screen simultaneously with the corresponding sound. The second sound-object association followed on the other side of the screen after 500ms. For both objects, visual stimuli were present for the duration of the sound clip (about 800ms).  In the testing trials, participants saw both objects simultaneously and heard only one sound. They completed the trial by selecting which of the two objects corresponded to the sound. The object-sound pairings were randomized across participants, as was the order of the conditions (except for the catch condition which was always placed in the middle of the testing sequence). We also randomized the on-screen position (left vs. right) of the two pictures on each testing trial.

@@

@@

For object distance, we found $\beta =$ `r c_coef`  ($p$ `r p_val(c_p)`), and this finding confirms the new prediction of our model, according to which, object distance also modulates success in word learning. Note, in particular, that increasing the visual similarity of the objects makes children succeed in learning the similar-sounding words. Finally, for the age group, we obtained  $\beta =$ `r age_coef` ($p$ `r p_val(age_p)`), showing that overall performance improves with age. The full output of the regression model is shown in Table 2.

@@

mods <- data.frame(models = c('model 1', 'model 2', 'model 3'),
                   struc = c("$\\sigma$\\textsubscript{L} only",
                             "$\\sigma$\\textsubscript{L} = $\\sigma$\\textsubscript{C}",
                             "$\\sigma$\\textsubscript{L} $\\neq$ $\\sigma$\\textsubscript{C}"),
                   param = c(1,1,2),
                   R = c(R2_model1, R2_model2, R2_model3),
                   sigS_C = c(mod1_ch_val,
                              mod2_ch_val,
                              mod3_ch_s_val
                              ),
                   sigO_C = c('--',
                              mod2_ch_val,
                              mod3_ch_o_val
                              ),
                   sigS_A = c(mod1_ad_val,
                              mod2_ad_val,
                              mod3_ad_s_val
                              ),
                   sigO_A = c('--',
                              mod2_ad_val,
                              mod3_ad_o_val

@@

kable(mods, format = "latex", escape = FALSE, booktabs = TRUE,
      linesep = "", format.args = list(big.mark = ","),
      caption = "Characteristics and performance of the models used in this study.",
      col.names = c("Model",  "Structure", "Param.", "R\\textsuperscript{2}", "$\\sigma$\\textsubscript{L}", "$\\sigma$\\textsubscript{C}", "$\\sigma$\\textsubscript{L}", "$\\sigma$\\textsubscript{C}")) %>%
  add_header_above(c("", "","","","Children" = 2, "Adults" = 2)) %>%
  column_spec(1, bold = TRUE) %>%
  kable_styling(position = "center")

@@

We next fit the three models obtained through expressions \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} to the participants' responses in each age group. The predictions of the models are shown \@ref(fig:allData). The parameter estimates (for $\sigma_L$ and $\sigma_C$) as well as models' goodness to fit (i.e., measured through $R^2$) are presented in Table \@ref(tab:models).

@@

We find in the literature two broad accounts of development in the Switch task: One that suggests *direct* development of the sound representation and one that hypothesizes *indirect* development of this representation through improvement in general cognitive resources. On the first account, the sound representation becomes more precise as learners refine the boundaries of their initially ambiguous phonetic categories and as they gain more experience with the functional role of these categories [@yoshida2009; @dietrich2007; @rost2009; @rost2010; @apfelbaum2011]. On the second account, the precision of sound encoding in the switch task improves as a result of the maturation of more general resources like the attentional and working memory capacity [@stager1997; @werker2004; @hofer2017]. Such improvement allows older children and adults to better encode the sound details while simultaneously matching these sounds to visual objects. Indeed, one recent meta-analysis of the switch task concluded that both changing representation precision and better memory/attention play a role in developmental changes [@tsui2019].

@@

Our model is compatible with both of these accounts. In our work, the probability distributions do not distinguish between the direct and indirect sources of uncertainty --- both are included. Indeed, part of the measured uncertainty reflects the learner's degrees of confidence in the phonetic/phonological boundaries (i.e., the direct account) and another part reflects a possible drop in perceptual acuity due to high cognitive load (i.e., the indirect account). Note, however, that the model (at least in its current format) is incapable of answering questions about the development of each of these sources of uncertainty separately or about their relative contribution to the global uncertainty.

@werker2005 proposed to explain development in the Switch task using their theory called Processing Rich Information from Multidimensional Interactive Representations (or PRIMIR) which attempts to explain various phenomena in early speech perception and word learning within a unified framework. PRIMIR posits that children initially try to attend to various features of the speech signal, regardless of whether or not these features are relevant to the task at hand. For example, when learning the meaning of similar sounds, infants are unsure what detail is most important to identify words (i.e., the phonemes), and will instead activate several aspects of the information simultaneously (including, for example, the gender of the speaker). The lack of selective attention leads to confusion and then to failure in the task.

According to PRIMIR, learning similar-sounding words becomes more robust over time as children develop abstract phonemic categories. The latter act as filters, allowing children to attend selectively to the important information. This account is also compatible with our model: Developing phonemic categories allows learners to better determine when a sound contrast signals a change in meaning (i.e., when this contrast straddles two categories as in "bin" vs. "din") and when a sound contrast does not change word meaning (i.e.,  when it instantiates a variation within the same category). In fact, learning to distinguish contrastive vs. non-contrastive pairs amounts to reducing the overlap between the probability distribution of two neighboring words.

@@

While most research has focused on sound representation specifically in analyzing the process of learning similar-sounding words, this work showed that the visual representation of the referent is equally important. Indeed, Model 1 --- which assumes that any visually discriminable contrast can be encoded unambiguously as separate referents --- failed to explain the data, whereas Model 2 and 3 --- which take into account visual ambiguity --- succeeded. As a consequence of this assumption, we found that just like word learning is modulated by the phonological similarity of the form, it is also modulated by the visual similarity of the semantic referents.

@@

There are a few limitations to this work. One is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-17 month-old). We selected this older age group to optimize the number and precision of the experimental measures (both are crucial to model fitting). Data collection involved presenting participants with several trials across four conditions in a between-subject design. It would have been challenging to obtain such measures with infants. That said, though we used data from older children, we still found clear developmental differences with adults, confirming and extending findings that the ability to distinguish similar-sounding words continues developing well beyond 17 months [@Fennell2014; @Mattock2010; @hazan2000].

@@

>>>>

header-includes:
   - \usepackage{tipa}
   - \usepackage[sortcites=false,sorting=none]{biblatex}
   - \usepackage{xcolor}

@@

figsintext        : no
figurelist        : yes
tablelist         : no
footnotelist      : no
lineno            : no

@@

```{r load_packages, include = FALSE}
library(papaja)
library(png)
library(grid)
library(ggplot2)
library(ggthemes)
library(xtable)
options(xtable.comment = FALSE)
library(purrr)
library(readr)
library(ggplot2)
#library(langcog)
library(boot)
#library(lazyeval)
library(dplyr)
library(tidyr)
library(wordbankr)
library(directlabels)
#library(scales)
library(stringr)
library(lmtest)
#library(rwebppl)
library(jsonlite)
library(nlme)
library(feather)
library(broom)
library(HDInterval)
library(BBmisc)
library(stargazer)
library(lme4)
library(kableExtra)
```

# Introduction

@@

The probabilistic account was used before to explain patterns of learning and development at the qualitative level [e.g.,@swingley2007]. However, it is crucial to have a precise computational instantiation of this account which would help us 1) test this theoretical hypothesis more directly and 2) identify the particular parameters that are the locus of developmental change.  One previous study attempted to provide such a computational instantiation [@hofer2017]. However, this previous work was designed with the goal of reproducing the results of a specific study [@pajak2016] which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.

@@

A similar probabilistic structure was used by @lewis2013 to model concept learning, and by @hofer2017 to model spoken word learning. However, the first study assumed that the sounds are heard unambiguously, and the second assumed the concepts are observed unambiguously. In our model, we assume that both labels and concepts are categories with possibly overlapping distributions. In other words, we allow the model to account for the --- more realistic --- possibility that an instances of a given categories (e.g.,"bin") can be mistaken for an instance of a neighboring category (e.g., "din"), albeit with a smaller probability. We assume, for simplicity, that this probability is captured by a normal distribution\footnote{\textcolor{red}{We used a normal distribution to simplify the mathematical derivations. This is obviously not aimed at providing a precise representation for the word-forms (and even less so for the visual objects), but as we shall in the results section, this simplified representation was enough to quantify the confusability of a given stimulus with its neighbors, which is the quantity we needed to predict the accuracy of word-object mapping in our task.}}:

@@

Finally, we assume there to be one-to-one mappings between concepts and labels and that observers have successfully learned these mappings during the exposure phase:
\begin{equation}\label{eq:mapping}
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{otherwise  }
\end{cases}
\end{equation}

@@

From the general expression \ref{eq:general}, we derive three exact analytical solutions instantiating different learning assumptions.

### Model 1

 Recall from expressions \ref{eq:object} and \ref{eq:sound} that $P(o|C)$ and $P(s|L)$ have parameters $\sigma_C$ and $\sigma_L$, respectively, that control for uncertainty. The first solution/model is derived by assuming that the labels are recovered from sounds with a certain level of uncertainty $\sigma_L > 0$, but that concepts are unambiguously recovered from the observed objects, i.e., $\sigma_C \rightarrow 0$. This assumption has been made --- whether implicitly or explicitly --- by most previous work in this line of research. For example, in @stager1997, the objects were quite dissimilar. Thus, the assumption that they were easily discriminated by infants seems relatively well justified. One important implication of this assumption is that only the similarity of word sounds modulates performance in word learning, not the similarity of the referents (as long as these referents are differentiated perceptually).

This assumption yields the following probability function of choosing the correct object $o_i$ given the correspondding label instance $s_i$, where $i \in \{1,2\}$ (see the Appendix for the full mathematical derivation):

\begin{equation} \label{eq:model1}
P(o_i|s_i)= \frac{1}{1 + e^{-\frac{\Delta s^2}{2\sigma_L^2}}}
\end{equation}

where $\Delta s = s_2-s_1$ is the perceptual sound distance between the pair of sounds that we refer to as $s_1$ and $s_2$. These distances were measured empirically as shown in Figure \@ref(fig:stim).

### Model 2

The second solution is derived by making the more general assumption that both the labels and the concepts are recovered with noise from the sounds and objects. We first introduce the simplifying assumption that the label-related uncertainty $\sigma_L$ and the concept-related uncertainty $\sigma_C$ are of a similar magnitude, i.e., $\sigma_C \approx \sigma_L = \sigma$. This assumption makes the prediction that the sound similarity and the object similarity impact word learning accuracy in exactly the same way. Furthermore, it allows us to study the behavior of the model with only one free parameter, an important consideration given the small number of datapoints available from any given infant experiment.

\begin{equation} \label{eq:model2}
P(o_i|s_i)= \frac{1 + e^{- \frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}}{1 + e^{-\frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}+ e^{-\frac{\Delta s^2}{2\sigma^2}} + e^{-\frac{\Delta o^2}{2\sigma^2}}}
\end{equation}

@@

\begin{equation} \label{eq:model3}
P(o_i|s_i)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}
\end{equation}

In order to understand the predictions of the models (especially the more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation} show simulations of the accuracy $P(o_i|s_i)$ as a function of the distinctiveness parameters ($\Delta s$ and $\Delta o$) and the uncertainty parameters $\sigma_L$ and $\sigma_C$.

@@

plot_simulation <- ggplot(simulations, aes(x=x, y=y, col=sigma)) + 
  geom_line() + 
  theme_few()+
  theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 8),
      aspect.ratio = 0.7
      )+
  #plot.margin=grid::unit(c(0,0,0,0), "mm")
  ylim(c(0.4,1))+
  geom_hline(yintercept = 0.50, linetype="dashed") +
  xlab(expression(Delta*"s")) + ylab(expression("P("*o['i']*"|"*s['i']*")")) +
  facet_grid(.~obj) +
  #facet_grid(.~object_distance) +
  scale_color_discrete(name = expression(sigma))

@@

### Stimuli and similarity rating
The sound stimuli were generated using the MBROLA Speech Synthesizer [@dutoit1996]. We generated three kinds of nonsense word pairs which varied in their degree of perceptual similarity to English speakers: 1) *different* pairs: "lif"/"neem" and "zem"/"doof", 2) *intermediate* pairs: "aka"/"ama" and "ada"/"aba", and 3) *similar* non-English pairs\footnote{For the intermediate/similar pairs, we made the choice of using a VCV (Vowel-Consonant-Vowel) structure in order to emphasize the phonemic difference in the minimal pairs, especially for the non-native contrasts. However, as one reviwer rightfully pointed out to us, this structure could influence word leaning performance since it is not common in English. Nevertheless, if we observed this effect, we would have seen differences in predictability between the intermediate/similar pairs on the one hand, and different pairs (which are phonotactically common in English) on the other hand. However, this was not the case, word learning accuracy was correctly predicted based on perceptual similarity alone.}: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic). For the simialr pairs, we used non-native sounds because this was a good way to decrease perceptual similarity for adults. In this respect, we took inspiration from the work of @pajak2016. We refer the reader to that paper for a lengthy discussion of the literature on (and implications for) L2 phoneme perception.

@@

### Design

@@

```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=4, fig.height=3, fig.cap = "Distances for sound and object pairs ($\\Delta s$ and $\\Delta o$, respectively) from an adult norming study. Data represent Likert values normalized to [0,1] interval. Error bars represent 95\\% confidence intervals."}

@@

In the exposure trials, participants saw two objects associated with their corresponding sounds. We presented the first object on the left side of the tablet's screen simultaneously with the corresponding sound. The second sound-object association followed on the other side of the screen after 500ms. For both objects, visual stimuli were present for the duration of the sound clip (about 800ms). During this phase, participant were asked to pay attention and try yo lean the words. In the testing trials, participants saw both objects simultaneously and heard only one sound. They completed the trial by selecting which of the two objects corresponded to the sound. The object-sound pairings were randomized across participants, as was the order of the conditions (except for the catch condition which was always placed in the middle of the testing sequence). We also randomized the on-screen position (left vs. right) of the two pictures on each testing trial.  The online experiment can be viewed at XXX

@@

```{r results='asis'}

#Binomoial test to show that children are not different from chance at the most difficult condition
rand_stat <- d_child_good %>%
  filter(sound_dist == "similar" & concept_dist == "similar")

myVar <- rand_stat$iscorrect
k <- sum(myVar)
n <- length(myVar)

myTest0 <- binom.test(k,n, 0.5)

rand_plus_stat <- d_child_good %>%
  filter(sound_dist == "similar" & concept_dist == "different")

myVar <- rand_plus_stat$iscorrect
k <- sum(myVar)
n <- length(myVar)

myTest1 <- binom.test(k,n, 0.5)

@@

For object distance, we found $\beta =$ `r c_coef`  ($p$ `r p_val(c_p)`), and this finding confirms the new prediction of our model, according to which, object distance also modulates performance in word learning. Finally, for the age group, we obtained  $\beta =$ `r age_coef` ($p$ `r p_val(age_p)`), showing that overall performance improves with age. The full output of the regression model is shown in Table 2.

In particular, while children were not different form chance in the most difficult condition when both the sounds and objects are similar . Note, however, the differe that the difference between the these two conditions was not itself

@@

mods <- data.frame(models = c('model 1', 'model 2', 'model 3'),
                   struc = c("$\\sigma$\\textsubscript{L} only",
                             "$\\sigma$\\textsubscript{L} = $\\sigma$\\textsubscript{C}",
                             "$\\sigma$\\textsubscript{L} $\\neq$ $\\sigma$\\textsubscript{C}"),
                   param = c(1,1,2),
                   R = c(R2_model1, R2_model2, R2_model3),
                   sigS_C = c(paste(mod1_ch_val, ' [', mod1_ch_conf1, ', ' , mod1_ch_conf2, ']', sep = ""),
                              paste(mod2_ch_val, ' [', mod2_ch_conf1, ', ' , mod2_ch_conf2, ']', sep = ""),
                              paste(mod3_ch_s_val, ' [', mod3_ch_s_conf1, ', ' , mod3_ch_s_conf2, ']', sep = "")
                              ),
                   sigO_C = c('--',
                              paste(mod2_ch_val, ' [', mod2_ch_conf1, ', ' , mod2_ch_conf2, ']', sep = ""),
                              paste(mod3_ch_o_val, ' [', mod3_ch_o_conf1, ', ' , mod3_ch_o_conf2, ']', sep = "")
                              ),
                   sigS_A = c(paste(mod1_ad_val, ' [', mod1_ad_conf1, ', ' , mod1_ad_conf2, ']', sep = ""),
                              paste(mod2_ad_val, ' [', mod2_ad_conf1, ', ' , mod2_ad_conf2, ']', sep = ""),
                              paste(mod3_ad_s_val, ' [', mod3_ad_s_conf1, ', ' , mod3_ad_s_conf2, ']', sep = "")
                              ),
                   sigO_A = c('--',
                              paste(mod2_ad_val, ' [', mod2_ad_conf1, ', ' , mod2_ad_conf2, ']', sep = ""),
                              paste(mod3_ad_o_val, ' [', mod3_ad_o_conf1, ', ' , mod3_ad_o_conf2, ']', sep = "")

@@

kable(mods, format = "latex", escape = FALSE, booktabs = TRUE,
      linesep = "", format.args = list(big.mark = ","),
      caption = "Characteristics and performance of the models used in this study. Value ranges represent 95\\% confidence intervals.",
      col.names = c("Model",  "Structure", "Param.", "R\\textsuperscript{2}", "$\\sigma$\\textsubscript{L}", "$\\sigma$\\textsubscript{C}", "$\\sigma$\\textsubscript{L}", "$\\sigma$\\textsubscript{C}")) %>%
  add_header_above(c("", "","","","Children" = 2, "Adults" = 2)) %>%
  column_spec(1, bold = TRUE) %>%
  kable_styling(position = "center", latex_options="scale_down")

@@

We next fit the three models obtained through expressions \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} to the participants' responses in each age group. The predictions of the models are shown \@ref(fig:allData). The parameter estimates (for $\sigma_L$ and $\sigma_C$) as well as models' goodness to fit (i.e., measured through $R^2$) are presented in Table \@ref(tab:models). \ Remmeber that, in our model, the fitted uncertainty parameters characterize the learners' general processing skills at a given time in development. Thus, they are understood to be the same across all stimuli within a given modality.

@@

More precisely, our model used the assumption that the ability to distinguish two stimuli perceptually leads to accurate mapping to two distinct objects, although this mapping can be noisy. On this account, apparent patterns of failure and success in retrieval tasks (such as ours) reflect different degrees of noise in the learned representations and not necessarily the presence/absence of these representations. With this assumption, the model was capable of accurately predicting behavior (including around-chance performance in the case of the most difficult contrasts)\footnote{That is, the case when both the sounds and objects are similar for children. Figure 6 shows that the confidence intervals include the chance value of 0.5.}, thus providing a proof of concept for the continuity hypothesis. The discontinuity hypothesis  --- which posits the absence of learning and not just retrieval difficulty --- cannot be ruled out by our model, but it is less parsimonious. We propose that the continuous hypothesis should be considered as a baseline; discontinuous development should only be posited if it deviates from this baseline.

We find in the literature two broad accounts of development in the Switch task: One that suggests *direct* development of the sound representation and one that hypothesizes *indirect* development of this representation through improvement in general cognitive resources. On the first account, the sound representation becomes more precise as learners refine the boundaries of their initially ambiguous phonetic categories and as they gain more experience with the functional role of these categories [@yoshida2009; @dietrich2007; @rost2009; @rost2010; @apfelbaum2011; @werker2005]. On the second account, the precision of sound encoding in the switch task improves as a result of the maturation of more general resources like the attentional and working memory capacity [@stager1997; @werker2004; @hofer2017]. Such improvement allows older children and adults to better encode the sound details while simultaneously matching these sounds to visual objects. Indeed, one recent meta-analysis of the switch task concluded that both changing representation precision and better memory/attention play a role in developmental changes [@tsui2019].

@@

<!---
@werker2005 proposed to explain development in the Switch task using their theory called Processing Rich Information from Multidimensional Interactive Representations (or PRIMIR) which attempts to explain various phenomena in early speech perception and word learning within a unified framework. PRIMIR posits that children initially try to attend to various features of the speech signal, regardless of whether or not these features are relevant to the task at hand. For example, when learning the meaning of similar sounds, infants are unsure what detail is most important to identify words (i.e., the phonemes), and will instead activate several aspects of the information simultaneously (including, for example, the gender of the speaker). The lack of selective attention leads to confusion and then to failure in the task.

According to PRIMIR, learning similar-sounding words becomes more robust over time as children develop abstract phonemic categories. The latter act as filters, allowing children to attend selectively to the important information. This account is also compatible with our model: Developing phonemic categories, by definition, means that learners become better at determining when a sound contrast signals a change in meaning (i.e., when this contrast straddles two categories as in "bin" vs. "din") and when a sound contrast does not change word meaning (i.e.,  when it instantiates a variation within the same category). In fact, learning to distinguish contrastive vs. non-contrastive pairs amounts to reducing the overlap between the probability distribution of two neighboring words. 
--->

In some sense, our model is compatible with both of these accounts. Indeed, the model aims at understanding *how* (by contrast to *what*) uncertainty can influence word learning. It characterizes and measures uncertainty in a rather global/coarse fashion, without committing to any specific source. Thus, it is compatible\footnote{Note the fact that our model is compatible with several previous accounts does not necessarily mean that these accounts are themeselves compatible with one another.} with direct accounts that posit uncertainty primarily stems from noisy phonological representations, and with the indirect account which suggests uncertainty primarily stems from a limitation in the general cognitive resources, hindering precise encoding in memory of subtle sounds under challenging conditions. Note that, since our goal was not to distinguish between these accounts, the model (at least in its current format) cannot answer questions about the development of each of these sources of uncertainty separately or about their relative contribution to the global uncertainty.

@@

While most research has focused on sound representation specifically in analyzing the process of learning similar-sounding words, this work showed that the visual representation of the referent is equally important. Indeed, Model 1 --- which assumes that any visually discriminable contrast can be encoded unambiguously as separate referents --- failed to explain the data, whereas Model 2 and 3 --- which take into account visual ambiguity --- succeeded. As a consequence of this assumption, we found that just like word learning is modulated by the phonological similarity of the form, it is also modulated by the visual similarity of the semantic referents.  This result is different from previous findings on the effect of the referents' similarity on the phonological development of the wordform [@Zhao2019; @fourtassi2019; @yeung09]. Our result is about wordform-referent mapping --- a different learning problem as it involves, in particular, the encoding of visual semantic/referent knowledge about the word (see @Zhao2019 for a detailed dsicussion). That said, these two questions can be related, albeit indirectly. For instance, while we did not model the process of phonological developmental per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.

@@

Our work found, among other things, that children have higher sound/phoneme uncertainty that adults do, but prior work have shown that children have good auditory encoding [@swingley2000; @swingley2002; @swingley2003]. These two findings are not in contradicton with each other. In this work, and as we explained above, the measured sound uncertainty includes various sources. One of these sources is perceptual uncertainty, i.e., the ability to perceptually distinguish a sound from other neighboring sounds (e.g., "bin" is perceptually different from "din"), and another source is categorical uncertainty, i.e., the ability to estimate phonological boundaries, e.g., "bin" and "din" straddle a phonological boundary, that is, they signal a change in meaning. The fact that children have a higher sound uncertainty than adults do,  does not necessarily mean this higher uncertainty is due to poorer perceptual encoding, only.  In fact, it is possible that much of the differential in uncertainty (compared to adults) is due to the categorical/phonological dimension which we know undergoes a process of reorganization and refinement across development. Thus, our finding that children have higher sound-related uncertainty does not contradict previous work showing children are capable of fine-grained speech perception (see @werker2005 for a similar view).

There are a few limitations to this work. One is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-17 month-old). We selected this older age group to optimize the number and precision of the experimental measures (both are crucial to model fitting). Data collection involved presenting participants with several trials across four conditions in a within-subject design. It would have been challenging to obtain such measures with infants. That said, though we used data from older children, we still found clear developmental differences with adults, confirming and extending findings that the ability to distinguish similar-sounding words continues developing well beyond 17 months [@Fennell2014; @Mattock2010; @hazan2000].

@@

# Appendix

Here we provide the full mathematical derivation the models' predictions. More specifically, we explain how the general Equation \ref{eq:general} leads to Equations \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} which represent our three Models.

Each of these Models instantiates an approximation of $P(o_i|s_i)$ which is the probability that, given a label instance $s_i$, a participant would choose the correct object $o_i$, as opposed to the incorrect object $o_{j}$, where $i, j \in \{1,2\}$ and $j = 1-i$.

We strat from the general expression of this probability as defined in Equation \ref{eq:general}. This expression can be normalized in our special case (i.e., a two-alternative-forced choice task) as follows:

$$P(o_i|s_i) = \frac{\sum_{C,L} P(s_i|L)P(L|C)P(o_i|C)}{\sum_{C,L}  P(s_i|L)P(L|C)P(o_i|C) + \sum_{C,L}  P(s_i|L)P(L|C)P(o_j|C)}.$$
Using the definition of $P(L|C)$ (given in Equation \ref{eq:mapping}) and the fact that we only have two possible categories in each modality ($L_1, L_2$ and $C_1, C_2$) we obtain:

\begin{equation} \label{eq:special}
P(o_i|s_i) = \frac{P(s_i|L_i)P(o_i|C_i) + P(s_i|L_j)P(o_i|C_j)}{[P(s_i|L_i)P(o_i|C_i) + P(s_i|L_j)P(o_i|C_j)] + [P(s_i|L_i)P(o_j|C_i) + P(s_i|L_j)P(o_j|C_j)]}
\end{equation}

In what follows, we compute the explicit expression of each conditional probability in Equation \ref{eq:special}.

$P(s_i | L_i)$ is the probability that the sound $s_i$ was sampled from its correct category $L_i$. Using the fact that we assumed in Equation \ref{eq:sound} that this probability follows a normal distribution $\mathcal{N}(\mu_C, \sigma^2_C)$, we have:

$$P(s_i|L_i) = \frac{1}{\sqrt{2\pi\sigma^2_{L_i}}}e^{-\frac{(s_i-\mu_{L_j})^2}{2\sigma^2_{L_i}}}.$$

We use the symplifying assumption that $\sigma_{L_i} = \sigma_L$, an uncertainty common to all labels. $\sigma_L$ can be understood as characterizing general speech processing skills (at a given time in development). We obtain the following expression:

$$P(s_i | L_i) = \frac{1}{\sqrt{2\pi\sigma^2_L}} e^{-\frac{(s_i-\mu_{L_j})^2}{2\sigma^2_L}}.$$

$s_i$ is supposed to be the prototyical instance of $L_i$, that is, $s_i=\mu_{L_j}$, leading to $$P(s_i | L_i) = \frac{1}{\sqrt{2\pi\sigma^2_L}}.$$

Similarly, $$P(o_i | C_i) = P(o_j | C_j) = \frac{1}{\sqrt{2\pi\sigma^2_C}}.$$

$P(s_i | L_j)$ is the probability that the sound $s_i$, though a perfect instance of $L_i$, could still be a mispronunced instance of the category $L_j$. The value of this probability depends on the extent to which the distributions of the categories $L_i$ and $L_j$ overlap with each other (Figure \@ref(fig:illus)). Using the normal distribution, we obtain the following expression: $$P(s_i| L_j) = \frac{1}{\sqrt{2\pi\sigma^2_L}} e^{-\frac{(s_i-s_j)^2}{2\sigma^2_L}} = \frac{1}{\sqrt{2\pi\sigma^2_L}} e^{-\frac{\Delta s^2}{2\sigma^2_L}}.$$

Similarly, $$P(o_i| C_j) = P(o_j| C_i) = \frac{1}{\sqrt{2\pi\sigma^2_C}} e^{-\frac{\Delta o^2}{2\sigma^2_C}} $$

Finally, we substitute all these expresisions in equation \ref{eq:special} above, leading to:
